---
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#STEPS OF DATA PRE - PROCESSING:
#1 Reading the csv file:
```{r}
data = read.csv("online_shoppers_intention.csv")
attach(data)
head(data)
tail(data)
```


#2 Checking the structure of the data:
```{r}
str(data)
```
#3 Summary
```{r}
summary(data)
```

#4 Checking missing data: There are no missing values in the dataset
```{r}
which(is.na(data))
which(is.null(data))
```
# Codes, if I want to check missing data for each variable
#data$Administrative[which(is.na(data$Administrative))]
#data$Administrative_Duration[which(is.na(data$Administrative_Duration))]

# Codes, if there would have been any missing value to be replaced by mean.

#data$Administrative = ifelse(is.na(data$Administrative),
#                             ave(data$Administrative, FUN = function(x) mean (x, na.rm = TRUE)),
#                             data$Administrative)


#5 Univariate Analysis: Checking the frequency distribution of the data for each variable.
```{r}
hist(data$Administrative,main = "Administrative Page visited by the user in that session", xlab = "Number of time administrative Page visited", ylab = "Count of users",xlim = c(0,30),breaks =30 ,col = "Blue")

#install.packages("moments")
library(moments)

#install.packages("nortest")
library(nortest)

#install.packages("goftest")
library(goftest)

# Measure of skewness
skewness(Administrative) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(Administrative) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.

Admlog<-log10(data$Administrative)

hist(Admlog,main = "Log10: Administrative Page visited by the user in that session", xlab = "Number of time administrative Page visited", ylab = "Count of users",xlim = c(0,2),breaks =10 ,col = "Blue")
```

```{r}
hist(data$Administrative_Duration,main = "Time spent on Administrative Page",xlab = "Time spent in seconds on Administrative Page", ylab = "Count of users",xlim = c(0,3400),breaks =25 ,col = "Blue")

# Measure of skewness
skewness(Administrative_Duration) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(Administrative_Duration) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Admdurlog<-log10(data$Administrative_Duration)

hist(Admdurlog,main = "Log10:Time spent on Administrative Page",xlab = "Time spent in seconds on Administrative Page", ylab = "Count of users",xlim = c(0,5),breaks =25 ,col = "Blue")

```

```{r}
hist(data$Informational,main = "Informational Page visited by the user in that session", xlab = "Number of time Informational Page visited", ylab = "Count of users",xlim = c(0,25),breaks =30 ,col = "Dark Green")

# Measure of skewness
skewness(Informational) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(Informational) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Inflog<-log10(data$Informational)

hist(Inflog,main = "Log10:Informational Page visited by the user in that session", xlab = "Number of time Informational Page visited", ylab = "Count of users",col = "Dark Green")
```

```{r}
hist(data$Informational_Duration,main = "Time spent on Informational Page",xlab = "Time spent in seconds on Informational Page", ylab = "Count of users",xlim = c(0,3000),breaks =25 ,col = "Dark Green")

# Measure of skewness
skewness(Informational_Duration) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(Informational_Duration) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Infdurlog<-log10(data$Informational_Duration)

hist(Infdurlog,main = "Log10: Time spent on Informational Page",xlab = "Time spent in seconds on Informational Page", ylab = "Count of users",xlim = c(0,4),breaks =25 ,col = "Dark Green")
```

```{r}
hist(data$ProductRelated,main = "Product Related Page visited by the user in that session", xlab = "Number of time Product Related Page visited", ylab = "Count of users",xlim = c(0,800),breaks =10 ,col = "Purple")

# Measure of skewness
skewness(ProductRelated) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(ProductRelated) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Prolog<-log10(data$ProductRelated)

hist(Prolog,main = "Log10:Product Related Page visited by the user in that session", xlab = "Number of time Product Related Page visited", ylab = "Count of users",xlim = c(0,3),breaks =25 ,col = "Purple")
```

```{r}
hist(data$ProductRelated_Duration,main = "Time spent on Product Related Page",xlab = "Time spent in seconds on Product Related Page", ylab = "Count of users",xlim = c(0,70000),breaks =50 ,col = "Purple")

# Measure of skewness
skewness(ProductRelated_Duration) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(ProductRelated_Duration) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Produrlog<-log10(data$ProductRelated_Duration)

hist(Produrlog,main = "Log10: Time spent on Product Related Page",xlab = "Time spent in seconds on Product Related Page", ylab = "Count of users",xlim = c(0,5),breaks =50 ,col = "Purple")
```

```{r}
hist(data$BounceRates,main = "Bounce Rate - Single Request Triggered", xlab = "Bounce Rate in Percentage", ylab = "Count of users",xlim = c(0,1),breaks =2 ,col = "Brown")

# Measure of skewness
skewness(BounceRates) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(BounceRates) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
BRlog<-log10(data$BounceRates)

hist(BRlog,main = "Log10: Bounce Rate - Single Request Triggered", xlab = "Bounce Rate in Percentage", ylab = "Count of users",col = "Brown")
```


```{r}
hist(data$ExitRates,main = "Exit Rate - Percentage of people who left the site from that page", xlab = "Exit Rate in Percentage", ylab = "Count of users",xlim = c(0,1),breaks =2 ,col = "Yellow")

# Measure of skewness
skewness(ExitRates) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(ExitRates) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
Exitlog<-log10(data$ExitRates)

hist(Exitlog,main = "Log10:Exit Rate - Percentage of people who left the site from that page", xlab = "Exit Rate in Percentage", ylab = "Count of users",col = "Yellow")
```

```{r}
hist(data$PageValues,main = "Page Values", xlab = "Average number of page visited", ylab = "Count of users",xlim = c(0,400),breaks =50 ,col = "Pink")
#Measure of skewness
skewness(PageValues) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(PageValues) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
PVlog<-log10(data$PageValues)

hist(PVlog,main = "Log10: Page Values", xlab = "Average number of page visited", ylab = "Count of users",col = "Pink")
```

```{r}
hist(data$SpecialDay,main = "Special Day", xlab = "Days close to any special day", ylab = "Count of users",col = "Red")
#Measure of skewness

skewness(PageValues) # If the data is normally distributed value of skewness should be 0. since,we got 1.96. That means the data is positively skewed.

kurtosis(PageValues) # Kurtosis value should be 3. since, we got higher than 3. There is a violation of normality and It is Leptokurtic i.e. thin curve.

#log10 function to solve problem of skewness - The data appears to be skewed towards right.After applying, log10 function the data appears to be normally distributed.
PVlog<-log10(PageValues)
```

```{r}
countsmonth<-table(data$Month)

barplot(countsmonth,main = "Distribution by Month", xlab = "Month of the visit",ylab = "Count of Sessions")
```

```{r}
countsOS<-table(data$OperatingSystems)
barplot(countsOS,main = "Distribution by Operating Systems", xlab = "Types of Operating System",ylab = "Count of Sessions")
```

```{r}
countbrowser<-table(data$Browser)
barplot(countbrowser,main = "Distribution by Browsers", xlab = "Different types of browsers used",ylab = "Count of Sessions")
```

```{r}
countregion<-table(data$Region)
barplot(countregion,main = "Distribution by Regions", xlab = "Regions",ylab = "Count of Sessions")
```

```{r}
countTrf<-table(data$TrafficType)
barplot(countTrf,main = "Distribution by Traffic Types", xlab = "Traffic Types",ylab = "Count of Sessions")
```

```{r}
countVist<-table(data$VisitorType)

barplot(countVist,main = "Distribution by Visitor Type", xlab = "Types of Visitors",ylab = "Count of Sessions",names.arg = c("New","Other","Returning"))
```

```{r}
countweekend<-table(data$Weekend)
barplot(countweekend,main = "Day of visit", xlab = "Visited on Weekdays Or Weekends",ylab = "Count of Sessions",names.arg = c("Weekdays","Weekends"))
```

```{r}
countrevenue<-table(data$Revenue)
barplot(countrevenue,main = "Purchased or Not", xlab = "Bought / Not Bought",ylab = "Count of Sessions",names.arg = c("Did Not Buy","Bought"))
```

#6 Bi - variate Analysis: Each categorical Variable by Revenue 
```{r}
countsmonth<-table(data$Revenue, data$Month)
barplot(countsmonth,main = "Distribution of Months By Revenue",
        xlab = "Months", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsmonth))
```

```{r}
countsOS<-table(data$Revenue, data$OperatingSystems)
barplot(countsOS,main = "Distribution of Operating System By Revenue",
        xlab = "Operating System", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsOS))
```
```{r}
countsbrowser<-table(data$Revenue, data$Browser)
barplot(countsbrowser,main = "Distribution of Browsers By Revenue",
        xlab = "Browsers", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsbrowser))
```

```{r}
countsregion<-table(data$Revenue, data$Region)
barplot(countsregion,main = "Distribution of Regions By Revenue",
        xlab = "Regions", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsregion))
```

```{r}
countstrf<-table(data$Revenue, data$TrafficType)
barplot(countstrf,main = "Distribution of Traffic Types By Revenue",
        xlab = "Traffic Types", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countstrf))
```

```{r}
countsvt<-table(data$Revenue, data$VisitorType)
barplot(countsvt,main = "Distribution of Visitor Types By Revenue",
        xlab = "Visitor Types", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsvt),names.arg = c("New","Other","Returning"))
```

```{r}
countswknd<-table(data$Revenue, data$Weekend)
barplot(countswknd,main = "Distribution of Days By Revenue",
        xlab = "Visited on Weekdays or Weekends", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countswknd),names.arg =c("Weekdays","Weekends"))
```

#7 Checking the outliers of the numerical data variables.

```{r}
boxplot(data$Administrative,col = "Orange",xlab  = "Administrative Page Visited",main="Outliers - Administration")

boxplot(data$Admlog,col = "Orange",xlab  = "Administrative Page Visited",main="Outliers:Log - Administration",range = (0))

boxplot(data$Administrative_Duration,col = "Orange",xlab  = "Administrative Duration",main="Outliers - Administration Duration")
boxplot(data$Admdurlog,col = "Orange",xlab  = "Administrative Duration",main="Outliers:Log - Administration Duration")

boxplot(data$Informational,col = "Blue",xlab  = "Informational Page Visited",main="Outliers - Informational")
boxplot(data$Inflog,col = "Blue",xlab  = "Informational Page Visited",main="Outliers:Log - Informational")


boxplot(data$Informational_Duration,col = "Blue",xlab  = "Informational Duration",main="Outliers - Informational Duration")
boxplot(data$Infdurlog,col = "Blue",xlab  = "Informational Duration",main="Outliers:Log - Informational Duration")


boxplot(data$ProductRelated,col = "Red",xlab  = "Product Related Page Visited",main="Outliers - Product Related")
boxplot(data$Prolog,col = "Red",xlab  = "Product Related Page Visited",main="Outliers:Log - Product Related")

boxplot(data$ProductRelated_Duration,col = "Red",xlab  = "Product Related Duration",main="Outliers - Product Relate Duration")
boxplot(data$Produrlog,col = "Red",xlab  = "Product Related Duration",main="Outliers:Log - Product Relate Duration")

boxplot(data$BounceRates,col = "Green",xlab  = "Bounce Rates",main="Outliers - Bounce Rates")
boxplot(data$BRlog,col = "Green",xlab  = "Bounce Rates",main="Outliers:Log - Bounce Rates")

boxplot(data$ExitRates,col = "Blue",xlab  = "Exit Rates",main="Outliers - Exit Rates")
boxplot(data$Exitlog,col = "Blue",xlab  = "Exit Rates",main="Outliers:Log - Exit Rates")

boxplot(data$PageValues,col = "Yellow",xlab  = "Page Values",main="Outliers - Page Values")
boxplot(data$PVlog,col = "Yellow",xlab  = "Page Values",main="Outliers:Log - Page Values")

```

#9 To find the correlation of all the variables with the class variable, i.e. "Revenue". But before that I have to convert the categorical variable into numerical variable.
```{r}
# Converting the categorical variables in numbers, because we want all the variables to be numeric for the correlation
# Month is already factor variable, but I am converting the lables with the correct numerical number for each month
data$Month = factor(data$Month,
                    levels = c('Feb', 'Mar','May','June','Jul','Aug','Sep','Oct','Nov','Dec'),
                    labels = c(2,3,5,6,7,8,9,10,11,12))

# Converting Month into numerical variable:
data$Month=as.numeric(data$Month)

# Visitor Type is already factor variable, but I am converting the lables with the descending numerical order 
data$VisitorType = factor(data$VisitorType,
                    levels = c('Returning_Visitor', 'New_Visitor','Other'),
                    labels = c(1,2,3))

data$VisitorType=as.numeric(data$VisitorType)

# Converting Weekend into numerical value. I am not converting Revenue into numerical because it is the class variable
data$Weekend=as.numeric(data$Weekend)
str(data)

#install.packages("corrplot")
library(corrplot)
correlation<-cor(data, method = "pearson")
corrplot(correlation,method = "circle")
corrplot.mixed(correlation,lower.col = 'black',number.cex=0.75,tl.cex=0.50)
```
