---
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#STEPS OF DATA PRE - PROCESSING:
#1 Reading the csv file:
```{r}
data = read.csv("online_shoppers_intention.csv")
attach(data)
head(data)
```


#2 Checking the structure of the data:
```{r}
str(data)
```
#3 Summary
```{r}
summary(data)
```

#4 Checking missing data: There are no missing values in the dataset
```{r}
which(is.na(data))
which(is.null(data))
```
# Codes, if I want to check missing data for each variable
#data$Administrative[which(is.na(data$Administrative))]
#data$Administrative_Duration[which(is.na(data$Administrative_Duration))]

# Codes, if there would have been any missing value to be replaced by mean.

#data$Administrative = ifelse(is.na(data$Administrative),
#                             ave(data$Administrative, FUN = function(x) mean (x, na.rm = TRUE)),
#                             data$Administrative)


#5 Univariate Analysis: Checking the frequency distribution of the data for each variable.
```{r}
hist(data$Administrative,main = "Administrative Page visited by the user in that session", xlab = "Number of time administrative Page visited", ylab = "Count of users",xlim = c(0,30),breaks =30 ,col = "Blue")
```

```{r}
hist(data$Administrative_Duration,main = "Time spent on Administrative Page",xlab = "Time spent in seconds on Administrative Page", ylab = "Count of users",xlim = c(0,3400),breaks =25 ,col = "Blue")
```

```{r}
hist(data$Informational,main = "Informational Page visited by the user in that session", xlab = "Number of time Informational Page visited", ylab = "Count of users",xlim = c(0,25),breaks =30 ,col = "Dark Green")
```

```{r}
hist(data$Informational_Duration,main = "Time spent on Informational Page",xlab = "Time spent in seconds on Informational Page", ylab = "Count of users",xlim = c(0,3000),breaks =25 ,col = "Dark Green")
```

```{r}
hist(data$ProductRelated,main = "Product Related Page visited by the user in that session", xlab = "Number of time Product Related Page visited", ylab = "Count of users",xlim = c(0,800),breaks =10 ,col = "Purple")
```

```{r}
hist(data$ProductRelated_Duration,main = "Time spent on Product Related Page",xlab = "Time spent in seconds on Product Related Page", ylab = "Count of users",xlim = c(0,70000),breaks =50 ,col = "Purple")
```

```{r}
hist(data$BounceRates,main = "Bounce Rate - Single Request Triggered", xlab = "Bounce Rate in Percentage", ylab = "Count of users",xlim = c(0,1),breaks =2 ,col = "Brown")
```

```{r}
hist(data$ExitRates,main = "Exit Rate - Percentage of people who left the site from that page", xlab = "Exit Rate in Percentage", ylab = "Count of users",xlim = c(0,1),breaks =2 ,col = "Yellow")
```

```{r}
hist(data$PageValues,main = "Page Values", xlab = "Average number of page visited", ylab = "Count of users",xlim = c(0,400),breaks =50 ,col = "Pink")
```

hist(data$SpecialDay)

```{r}
countsmonth<-table(data$Month)

barplot(countsmonth,main = "Distribution by Month", xlab = "Month of the visit",ylab = "Count of Sessions",names.arg = c("Feb","March","May","June","July","Aug","Sept","Oct","Nov","Dec"))
```

```{r}
countsOS<-table(data$OperatingSystems)
barplot(countsOS,main = "Distribution by Operating Systems", xlab = "Types of Operating System",ylab = "Count of Sessions")
```

```{r}
countbrowser<-table(data$Browser)
barplot(countbrowser,main = "Distribution by Browsers", xlab = "Different types of browsers used",ylab = "Count of Sessions")
```

```{r}
countregion<-table(data$Region)
barplot(countregion,main = "Distribution by Regions", xlab = "Regions",ylab = "Count of Sessions")
```

```{r}
countTrf<-table(data$TrafficType)
barplot(countTrf,main = "Distribution by Traffic Types", xlab = "Traffic Types",ylab = "Count of Sessions")
```

```{r}
countVist<-table(data$VisitorType)

barplot(countVist,main = "Distribution by Visitor Type", xlab = "Types of Visitors",ylab = "Count of Sessions",names.arg = c("New","Other","Returning"))
```

```{r}
countweekend<-table(data$Weekend)
barplot(countweekend,main = "Day of visit", xlab = "Visited on Weekdays Or Weekends",ylab = "Count of Sessions",names.arg = c("Weekdays","Weekends"))
```

```{r}
countrevenue<-table(data$Revenue)
barplot(countrevenue,main = "Purchased or Not", xlab = "Bought / Not Bought",ylab = "Count of Sessions",names.arg = c("Did Not Buy","Bought"))
```

#6 Bi - variate Analysis: Each categorical Variable by Revenue 
```{r}
countsmonth<-table(data$Revenue, data$Month)
barplot(countsmonth,main = "Distribution of Months By Revenue",
        xlab = "Months", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsmonth),names.arg =c("Feb","Mar","May","June","Jul","Aug","Sep","Oct","Nov","Dec"))
```

```{r}
countsOS<-table(data$Revenue, data$OperatingSystems)
barplot(countsOS,main = "Distribution of Operating System By Revenue",
        xlab = "Operating System", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsOS))
```
```{r}
countsbrowser<-table(data$Revenue, data$Browser)
barplot(countsbrowser,main = "Distribution of Browsers By Revenue",
        xlab = "Browsers", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsbrowser))
```
```{r}
countsregion<-table(data$Revenue, data$Region)
barplot(countsregion,main = "Distribution of Regions By Revenue",
        xlab = "Regions", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsregion))
```
```{r}
countstrf<-table(data$Revenue, data$TrafficType)
barplot(countstrf,main = "Distribution of Traffic Types By Revenue",
        xlab = "Traffic Types", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countstrf))
```
```{r}
countsvt<-table(data$Revenue, data$VisitorType)
barplot(countsvt,main = "Distribution of Visitor Types By Revenue",
        xlab = "Visitor Types", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countsvt),names.arg = c("New","Other","Returning"))
```
```{r}
countswknd<-table(data$Revenue, data$Weekend)
barplot(countswknd,main = "Distribution of Days By Revenue",
        xlab = "Visited on Weekdays or Weekends", col = c("darkblue", "Red"),
        ylab = "Count of Sessions",legend =rownames(countswknd),names.arg =c("Weekdays","Weekends"))
```

#7 Checking the outliers of data and normalised data

```{r}
boxplot(data$Administrative,col = "Orange",xlab  = "Administrative Page Visited",main="Outliers - Administration")

boxplot(data$Administrative_Duration,col = "Orange",xlab  = "Administrative Duration",main="Outliers - Administration Duration")

boxplot(data$Informational,col = "Blue",xlab  = "Informational Page Visited",main="Outliers - Informational")

boxplot(data$Informational_Duration,col = "Blue",xlab  = "Informational Duration",main="Outliers - Informational Duration")

boxplot(data$ProductRelated,col = "Red",xlab  = "Product Related Page Visited",main="Outliers - Product Related")

boxplot(data$ProductRelated_Duration,col = "Red",xlab  = "Product Related Duration",main="Outliers - Product Relate Duration")

boxplot(data$BounceRates,col = "Green",xlab  = "Bounce Rates",main="Outliers - Bounce Rates")

boxplot(data$ExitRates,col = "Blue",xlab  = "Exit Rates",main="Outliers - Exit Rates")

boxplot(data$PageValues,col = "Yellow",xlab  = "Page Values",main="Outliers - Page Values")

boxplot(data$SpecialDay,col = "Black",xlab  = "Special Day",main="Outliers - Special Day")

```
